Deep Learning for Automatic Speech Recognition

### 2015-04-21 Presentation/Presentation.tex
Cleaned up inconsistent periods

	\begin{center}
		Use N-gram language model, CD-DNN-HMM for acoustic model
	\end{center}
\end{frame}

@@

	Initialization:
	\begin{itemize}
		\item Find the best tying of triphone states
		\item Deal with some book keeping
		\item Train a CD-GMM-HMM using those states.
		\item Convert CD-GMM-HMM into CD-DNN-HMM keeping senone structure
		\item Apply pre-training algorithm on CD-DNN-HMM
	\end{itemize}

@@

	\begin{center}
		Need to understand Restricted Boltzmann Machines (RBMs) and Deep Belief Networks (DBNs)
	\end{center}

@@

	\begin{center}
		For purpose of this talk, stack RBMs on top of one another to get a DBN
	\end{center}

@@

	Metrics
	\begin{itemize}
		\item Sentence Error Rate (SER): Incorrect sentences (at least one word wrong) out of total sentences.
		\item Word Error Rate (WER): Levenshtein based measure of number of substitutions, deletions, and insertions relative to total words.
		\item Phoneme Error Rate (PER): Incorrect phonemes out of total phonemes
	\end{itemize}

@@

\begin{frame}{Experimental Results}
	\begin{center}
		Hinton et al. \textit{Deep Neural Networks for Acoustics Modeling in Speech Recognition: The shared views of four research groups} 
	\end{center}

@@

	\begin{center}
		Neural Networks are promising alternative to GMMs for acoustic modeling in ASR. But they have computational limitations \newline (e.g., not easily parallelizable across clusters)
	\end{center}

>>>>

	\begin{center}
		Use N-gram language model, CD-DNN-HMM for acoustic model.
	\end{center}
\end{frame}

@@

	Initialization:
	\begin{itemize}
		\item Find the best tying of triphone states
		\item Deal with some book keeping
		\item Train a CD-GMM-HMM using those states
		\item Convert CD-GMM-HMM into CD-DNN-HMM keeping senone structure
		\item Apply pre-training algorithm on CD-DNN-HMM
	\end{itemize}

@@

	\begin{center}
		Need to understand Restricted Boltzmann Machines (RBMs) and Deep Belief Networks (DBNs).
	\end{center}

@@

	\begin{center}
		For purpose of this talk, stack RBMs on top of one another to get a DBN.
	\end{center}

@@

	Metrics
	\begin{itemize}
		\item Sentence Error Rate (SER): Incorrect sentences (at least one word wrong) out of total sentences.
		\item Word Error Rate (WER): Levenshtein based measure of number of substitutions, deletions, and insertions relative to total words.
		\item Phoneme Error Rate (PER): Incorrect phonemes out of total phonemes.
	\end{itemize}

@@

\begin{frame}{Experimental Results}
	\begin{center}
		Hinton et al. \textit{Deep Neural Networks for Acoustics Modeling in Speech Recognition: The shared views of four research groups}:
	\end{center}

@@

	\begin{center}
		Neural Networks are promising alternative to GMMs for acoustic modeling in ASR. But they have computational limitations \newline (e.g., not easily parallelizable across clusters).
	\end{center}
